\documentclass[letterpaper,11pt]{article}

\usepackage[T1]{fontenc}
\usepackage[rm]{merriweather} % Merriweather font
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{xcolor} % For HTML colors
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{setspace} % For line spacing
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins for a cleaner, well-spaced look
\addtolength{\oddsidemargin}{-0.3in}
\addtolength{\evensidemargin}{-0.3in}
\addtolength{\textwidth}{0.6in}
\addtolength{\topmargin}{-0.4in}
\addtolength{\textheight}{0.8in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% --- Custom Colors ---
\definecolor{SectionBlue}{HTML}{2079c7}
% Changed grey darker so it is fully visible but distinct from black
\definecolor{TextGrey}{HTML}{333333} 
\definecolor{HighlightBlack}{HTML}{000000} % For highlights
\definecolor{LightLine}{HTML}{cccccc}

% --- Formatting ---
% Increased line spacing slightly to make each line breathe more
\setstretch{1.20} 
\color{TextGrey}

% Define the vertical bar before section text (approximate a thick pipe `❚`)
% Reduced standard spacing before/after section headers to make sections tighter
\titleformat{\section}{
  \vspace{2pt}\color{SectionBlue}\scshape\raggedright\large\bfseries % Tightened spacing here
}{\color{SectionBlue}\rule[-1pt]{4pt}{10pt}\hspace{8pt}}{0em}{}[\vspace{-2pt}]

\pdfgentounicode=1

% --- Custom Commands ---

% Ensure all text inside custom commands forces the correct color
\newcommand{\resumeItem}[1]{
  \item\small{\textcolor{TextGrey}{#1}} % Removed custom vspace after bullets
}

\newcommand{\hl}[1]{\textcolor{HighlightBlack}{\textbf{#1}}}
\newcommand{\hlit}[1]{\textcolor{HighlightBlack}{\textit{#1}}}

\newcommand{\resumeSubheading}[3]{
  \vspace{2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \hl{#1} \quad \hlit{#2} & \textcolor{TextGrey}{\small #3} \\
    \end{tabular*}\vspace{0pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \vspace{0pt}\item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \hl{#1} \quad \textcolor{TextGrey}{\textit{\small #2}} & \\
    \end{tabular*}\vspace{0pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in, label={\textcolor{TextGrey}{\vcenter{\hbox{\tiny$\bullet$}}}}] \vspace{-2pt} }
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\color{TextGrey} % Start document with base grey color

%----------HEADING----------
\noindent\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}l@{}}
\begin{minipage}[t]{0.65\textwidth}
    % Name is now in Title Case, Black, and slightly smaller
    {\Large \color{HighlightBlack} \textbf{Riyaz Pasha Mohammed}} \\ 
    {\normalsize \textcolor{TextGrey}{Senior Software Engineer $|$ Full Stack (Backend Heavy)}}
\end{minipage} &
\begin{minipage}[t]{0.35\textwidth}
    \raggedleft \small \textcolor{TextGrey}{
    Hyderabad, India \\
    \hl{+91 90009 67748} \\
    \href{mailto:riyazpasha880@gmail.com}{\textcolor{HighlightBlack}{riyazpasha880@gmail.com}} \\
    \href{https://linkedin.com/in/riyazpasha880}{\textcolor{HighlightBlack}{linkedin.com/in/riyazpasha880}}
    }
\end{minipage}
\end{tabular*}
\vspace{2pt}

\vspace{0pt} \hrule height 0.5pt \color{LightLine} \vspace{0pt} % Tightened gap under the line
\color{TextGrey}

%-----------SUMMARY-----------
\section*{SUMMARY}
\small{\textcolor{TextGrey}{Senior Software Engineer with 6+ years of experience building and modernizing high-traffic web and mobile applications at ThoughtWorks and Everest Engineering. Specializes in \hl{Spring Boot}, \hl{ExpressJS}, \hl{React}, \hl{React Native}, \hl{TypeScript}, \hl{Java}, and \hl{AWS} cloud-native architectures. Delivered measurable impact: cut API latency by \hl{67\%}, reduced CI build times by $\sim$\hl{35\%}, and integrated AI-driven automation into production systems. Passionate about clean architecture, TDD, and engineering quality.}}

%-----------EXPERIENCE-----------
\section*{EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Everest Engineering}{Software Craftsperson}{OCT 2022 - PRESENT}
      \resumeItemListStart
        \resumeItem{Developed scalable backend services for a construction platform using \hl{Spring Boot} and \hl{PostgreSQL}, managing budget utilization, work progress, and material delivery tracking.}
        \resumeItem{Integrated \hl{Azure AI Document Intelligence} to automate invoice data extraction, reducing manual data entry errors and improving ingestion accuracy.}
        \resumeItem{Optimized frontend performance via \hl{TanStack Query} and architecture refactoring, reducing page load times by $\sim$\hl{40\%}.}
        \resumeItem{Streamlined CI/CD pipelines in \hl{GitHub Actions}, reducing pipeline runtime by $\sim$\hl{35\%} and accelerating release cycles.}
        \resumeItem{Collaborated with stakeholders to translate business requirements into scalable APIs and iterative product improvements.}
      \resumeItemListEnd

    \resumeSubheading
      {ThoughtWorks}{Application Developer | Consultant}{JUL 2020 - OCT 2022}
      \resumeItemListStart
        \resumeItem{Reduced critical pricing API latency from $\sim$2s to $\sim$\hl{600ms} by optimizing \hl{SQL} queries, improving database indexing, and introducing a \hl{Redis} caching layer.}
        \resumeItem{Modernized legacy enterprise systems by migrating monolithic architectures to \hl{microservices} using \hl{AWS SQS}, \hl{Lambda}, and \hl{RDS/Aurora}.}
        \resumeItem{Migrated a SOAP-based university data exchange platform to \hl{RESTful APIs}, replacing API-key auth with \hl{Auth0} and cutting \hl{Jenkins} build time from 25+ to $\sim$\hl{12 minutes}.}
        \resumeItem{Practiced \hl{Agile/XP} — pair programming, TDD, continuous refactoring — across multiple client engagements.}
        \resumeItem{Mentored junior engineers through technical onboarding, code reviews, and knowledge-sharing sessions.}
      \resumeItemListEnd

    \resumeSubheading
      {ThoughtWorks}{Application Developer | Consultant Graduate}{JUL 2019 - JUL 2020}
      \resumeItemListStart
        \resumeItem{Delivered production-ready features for legacy modernization projects using \hl{Java} and \hl{TDD}; improved system stability by increasing unit and integration test coverage.}
        \resumeItem{Supported production deployments and collaborated on debugging and resolution of live issues.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section*{KEY PROJECTS}
    \resumeSubHeadingListStart
      
      \resumeProjectHeading
          {Construction Project Management Platform}{React $\cdot$ TypeScript $\cdot$ Spring Boot $\cdot$ PostgreSQL $\cdot$ Azure AI Document Intelligence}
          \resumeItemListStart
            \resumeItem{Designed backend workflows to track construction progress at building-floor granularity, improving operational visibility for site engineers.}
            \resumeItem{Implemented schedule vs. delivery reconciliation logic to identify missing or excess materials and validate delivery accuracy.}
            \resumeItem{Built scalable REST APIs with validation and error handling to support both web and mobile clients.}
            \resumeItem{Refactored frontend into a modular, maintainable architecture, reducing complexity and improving long-term extensibility.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {Legacy Modernization -- Pricing Application}{Java $\cdot$ Spring Boot $\cdot$ WebFlux $\cdot$ PostgreSQL $\cdot$ Redis $\cdot$ JUnit}
          \resumeItemListStart
            \resumeItem{Owned end-to-end modernization of two critical pricing microservices to production-ready Spring WebFlux services.}
            \resumeItem{Developed JMX-based performance testing scripts to validate latency improvements under production-like traffic.}
            \resumeItem{Improved code quality by resolving \hl{SonarQube} issues and increasing unit and integration test coverage.}
            \resumeItem{Conducted onboarding and knowledge-sharing sessions to improve team ramp-up and engineering consistency.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {Payments Application}{React Native $\cdot$ JavaScript}
          \resumeItemListStart
            \resumeItem{Owned and implemented two major end-to-end business flows — UI, validations, API integration, and edge-case handling.}
            \resumeItem{Led a development stream coordinating tasks across team members and ensuring timely sprint delivery.}
            \resumeItem{Conducted requirement analysis and delivered solutions backed by POCs to validate feasibility before implementation.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section*{SKILLS}
 \vspace{2pt}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \hl{Languages:}\quad \textcolor{TextGrey}{Java, TypeScript, JavaScript, SQL} \\ \vspace{2pt}
     \hl{Backend:}\quad \textcolor{TextGrey}{Spring Boot, WebFlux, Node.js, Express.js, Hibernate, REST APIs, Microservices} \\ \vspace{2pt}
     \hl{Frontend:}\quad \textcolor{TextGrey}{React, Next.js, React Native, Redux, TanStack Query} \\ \vspace{2pt}
     \hl{Cloud \& DevOps:}\quad \textcolor{TextGrey}{AWS (Lambda, SQS, RDS, Aurora), Docker, Serverless, Jenkins, GitHub Actions} \\ \vspace{2pt}
     \hl{Databases:}\quad \textcolor{TextGrey}{PostgreSQL, MongoDB, Redis, DynamoDB} \\ \vspace{2pt}
     \hl{Testing:}\quad \textcolor{TextGrey}{JUnit, Jest, Playwright, Mocha, Chai, SonarQube, Git, TDD}
    }}
 \end{itemize}

%-----------CERTIFICATIONS-----------
\section*{CERTIFICATIONS}
  \vspace{2pt}
  \begin{itemize}[leftmargin=0.2in, label={\textcolor{TextGrey}{\vcenter{\hbox{\tiny$\bullet$}}}}]
    \small{\item{
     \textcolor{TextGrey}{Stripe Certified Professional Developer}
    }}
    \small{\item{
     \textcolor{TextGrey}{Stripe Certified Billing Developer}
    }}
  \end{itemize}

%-------------------------------------------
\end{document}
